---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# The `airac` package

<!-- badges: start -->
<!-- badges: end -->

The `airac` package helps with determining the ICAO's AIRAC ID or the relevant
date intervals as used internationally and by the data services of the
European Network Manager.

AIRAC stands for Aeronautical Information Regulation and Control and it indicates
the period used to publish and disseminate changes to [aeronautical data][aip].

[aip]: <https://en.wikipedia.org/wiki/Aeronautical_Information_Publication> "Aeronautical Information Publication"

## Installation

You can install the development version of airac like so:

```{r eval=FALSE}
library(remotes)
install_github("euctrl-pru/pruatlas")
```

## Example

You may be interested to know which period corresponfs to AIRAC '2307'

```{r example}
library(airac)

airac_interval("2307")
```

or which AIRAC number is needed to download data on 1st Feb 2023 from EUROCONTROL's
Network Manager DDR2 repository:

```{r example-nm}
library(airac)

cfmu_airac("2023-02-01")
```


# Development

In order to build the relevant `pkgdown` web pages, execute the following code:

```{r, eval=FALSE}

# How to build the pakgdown from behind proxied Internet
library(withr)
library(pkgdown)

with_options(list(pkgdown.internet = FALSE),
             build_site())
```

Note that the pkgdown website is generated in `docs/` which is ignored by git.
So if you want to publish a new version of the package website, you need
to force add `docs/`.
it will then be served by GitHub Pages as per repo configuration.
